---
title: "Analy 510 52 Assignment 7"
author: "Team 3-Chak Lam Cheong, Minglu Li,Haotian Pei,Ruoxi Pei,Meiyao Li,Peng Gong"
date: "December 17, 2017"
output: html_document
---
#Peng Gong
## Populate the missing values in the Area variable with an appropriate values (Birmingham, Coventry, Dudley, Sandwell, Solihull, Walsall or Wolverhampton)
```{r}
library(tidyr)

Dirty_dataframe<-read.csv("C:/Users/Peng/Desktop/Harrisburg/ANLY 510 52/Dirty_Data.csv")

```



```{r}
colnames(Dirty_dataframe)
```

```{r}
str(Dirty_dataframe)
```
#Meiyao Li
## Remove special characters, padding (the white space before and after the text) from Street 1 and Street 2 variables. Make sure the first letters of street names are capitalized and the street denominations are following the same standard (for example, all streets are indicated as "str.", avenues as "ave.", etc.



```{r}
data_with_Area$Street = gsub("[^A-Za-z ]", " ",data_with_Area$Street)

data_with_Area$Street = gsub("(?<=[\\s])\\s*|^\\s+|\\s+$", "", data_with_Area$Street, perl=TRUE)

head(data_with_Area)

```


```{r}

data_with_Area$Street.2 = gsub("[^A-Za-z ]", " ",data_with_Area$Street.2)

data_with_Area$Street.2 = gsub("(?<=[\\s])\\s*|^\\s+|\\s+$", "", data_with_Area$Street.2, perl=TRUE)

head(data_with_Area)

```

```{r}

data_with_Area$Street = gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", data_with_Area$Street, perl=TRUE)
data_with_Area$Street.2 =  gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", data_with_Area$Street.2, perl=TRUE)

head(data_with_Area)

```




```{r}
head(Dirty_dataframe)
```

```{r}
library(tidyr)

Dirty_dataframe[Dirty_dataframe =="" ] <- NA
data_with_Area<-fill(Dirty_dataframe, "Area", .direction = c("down"))

head(data_with_Area)

```



